---
output:
  html_document:
    keep_md: yes
---
gameday
-------

A package that allows the user to extract data on NHL teams without using the browser. The RStudio interface is simple and intuitive to use.

### Installation
Install `gameday` from GitHub:

```{r, eval = F, echo = F}
devtools::install_github("dchiu911/gameday")
```
_Note that you need the `devtools` package to do this._

### Usage
At this point, `gameday` has two functions: `gday()` and `scores()`. We'll discuss each in turn.

Given a team and a date, we can call `gday(team, date)` to see whether that team plays on that date.

```{r}
library(gameday)

gday("devils", "2014-11-03")
```

What if we wanted to find all the final scores on a particular date? Then we can call `scores(date)` to return a `data.frame` with this information.

```{r}
scores("2014-11-15")
```

### Vignette
Further details can be found in the vignette for this package. To view it, run this command in the R console:

```{r, eval = FALSE}
browseVignettes("gameday")
```

Once there, you can click on the `HTML` link to get a nice introduction to `gameday`.
