---
title: "Overview of Gameday"
author: "Derek Chiu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview of Gameday}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

## Motivation

The `gameday` package provides a convenient way to extract simple information on NHL teams without using your internet browser. Sometimes we get distracted by extraneous information on the web and our attention is diverted. Using the functions in `gameday` can prevent this from happening!

## Usage
First we need to load the package.

```{r}
library(gameday)
```

### gday(team, date)

We can use this to check whether a specified team plays on a specified date. For example, a simple usage of this:

```{r}
# Checks whether the Canucks play today
gday()

# Checks whether the Bruins play tomorrow
gday("bruins", Sys.Date() + 1)
```

### scores(date)

We use this to lookup all the final scores on a particular date. For instance,
the `data.frame` output for the games on Remembrance Day are:
```{r}
# Lookup final scores on Remembrance Day
scores("2014-11-11")
```

There is more functionality we can utilize with `scores()`. We can look up all the winning teams of a certain hockey date. For this we'll employ `dplyr`.

```{r}
suppressPackageStartupMessages(library(dplyr))

# All winning teams on a particular date
score_data <- scores("2014-11-11")
score_data %>%
	mutate(winner = ifelse(home_score > away_score, as.character(home), as.character(away))) %>%
	select(winner)
```

Comparing the winners with the raw `score_data`, we see that indeed only the winning teams are shown.
